---
title: "Project-Groupassignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Group 4 Members:
### Manali Padhye, Kareem Rogers, Lin Li

##Slide 1 : Problem Introduction
####Determine the lowest cost path from each plant to each dealer, given their locations, existing VDC locations, demand by each dealer, the cost of handling and transportation.


##Slide 2 : Assumptions
####Assumptions:
####1. 2Plant to 2Dearlers: Plant1:3A,Plant2:FF, Dealer1:21720, Dealer2:21716.
####2. Only consider two types of shipping methods:AV and Truck.
####Results: 
####The result will show the total cost of shipping and the number of cars shipped through VDC and shipping method.

##Slide 3 : Calculation of Distances

###Calculation of Distance Plant1 to VDC1-5.

```{r}
library(dplyr)
library(sf)
library(lwgeom)
# Create example data frame the distance between plant1 3A and VDC 3F	4J	7J	7M	BC.
df <- data.frame(latitude = c(32.48,22.51,21.90,21.93,20.16,29.50
),
                 longitude = c(-178.36,172.08,163.14,169.40,170.06,171.76
))

# COnvert to sf object
df_sf <- st_as_sf(df, coords = c("longitude", "latitude"))

# Set the projection as ESPG 4326 (long_lat)
st_crs(df_sf) <- 4326

# Apply the st_distance function
dist_m <- st_distance(df_sf)

# Combine with df
df2 <- df %>% mutate(`3A-3A` = as.numeric(dist_m[,1]), 
         `3A-VDC1` = as.numeric(dist_m[,2]),
         `3A-VDC2` = as.numeric(dist_m[,3]),
         `3A-VDC3` = as.numeric(dist_m[,4]),
         `3A-VDC4` = as.numeric(dist_m[,5]),
         `3A-VDC5` = as.numeric(dist_m[,6]))
         
# Replace 0 with NA
df2/1610

```
###Result:The distance between Plant 3A and VDC 3F	4J	7J	7M	BC are which are 902	1348	1045	1109	621 miles.

###Calculation of Distance2 VDC1-5 to Dealer1

```{r}
library(dplyr)
library(sf)
library(lwgeom)
# Create example data frame the distance between Dealer 21720 and VDC 3F	4J	7J	7M	BC.
df <- data.frame(latitude = c(19.78,22.51,21.90,21.93,20.16,29.50
),
                 longitude = c(160.99,172.08,163.14,169.40,170.06,171.76
))

# COnvert to sf object
df_sf <- st_as_sf(df, coords = c("longitude", "latitude"))

# Set the projection as ESPG 4326 (long_lat)
st_crs(df_sf) <- 4326

# Apply the st_distance function
dist_m <- st_distance(df_sf)

# Combine with df
df2 <- df %>% mutate(`D1-D1` = as.numeric(dist_m[,1]), 
         `D1-VDC1` = as.numeric(dist_m[,2]),
         `D1-VDC2` = as.numeric(dist_m[,3]),
         `D1-VDC3` = as.numeric(dist_m[,4]),
         `D1-VDC4` = as.numeric(dist_m[,5]),
         `D1-VDC5` = as.numeric(dist_m[,6]))
         
# Replace 0 with NA
df2/1610
```

###Result:The distance between Dealer to VDC1-5 are 1190531.8, 324279.7, 906857.7, 950142.2, 1530652.3. which are 739	201	563	590	951 miles.

###Calculation of Distance3 Plant2 to VDC1-5.

```{r}
library(dplyr)
library(sf)
library(lwgeom)
# Create example data frame the distance between plant2 FF and VDC 3F	4J	7J	7M	BC.
df <- data.frame(latitude = c(19.57,22.51,21.90,21.93,20.16,29.50
),
                 longitude = c(170.72,172.08,163.14,169.40,170.06,171.76
))

# COnvert to sf object
df_sf <- st_as_sf(df, coords = c("longitude", "latitude"))

# Set the projection as ESPG 4326 (long_lat)
st_crs(df_sf) <- 4326

# Apply the st_distance function
dist_m <- st_distance(df_sf)

# Combine with df
df2 <- df %>% mutate(`FF-FF` = as.numeric(dist_m[,1]), 
         `FF-VDC1` = as.numeric(dist_m[,2]),
         `FF-VDC2` = as.numeric(dist_m[,3]),
         `FF-VDC3` = as.numeric(dist_m[,4]),
         `FF-VDC4` = as.numeric(dist_m[,5]),
         `FF-VDC5` = as.numeric(dist_m[,6]))
         
# Replace 0 with NA
df2/1610
```

###Result:The distance between plant FF to VDC 3F	4J	7J	7M	BC are 220, 516, 183, 59, 686 miles.

###Calculation of Distance4 VDC1-5 to Dealer2.

```{r}
library(dplyr)
library(sf)
library(lwgeom)
# Create example data frame the distance between Dealer 21716 and VDC 3F	4J	7J	7M	BC.
df <- data.frame(latitude = c(31.47,22.51,21.90,21.93,20.16,29.50
),
                 longitude = c(166.08,172.08,163.14,169.40,170.06,171.76
))

# COnvert to sf object
df_sf <- st_as_sf(df, coords = c("longitude", "latitude"))

# Set the projection as ESPG 4326 (long_lat)
st_crs(df_sf) <- 4326

# Apply the st_distance function
dist_m <- st_distance(df_sf)

# Combine with df
df2 <- df %>% mutate(`D2-D2` = as.numeric(dist_m[,1]), 
         `D2-VDC1` = as.numeric(dist_m[,2]),
         `D2-VDC2` = as.numeric(dist_m[,3]),
         `D2-VDC3` = as.numeric(dist_m[,4]),
         `D2-VDC4` = as.numeric(dist_m[,5]),
         `D2-VDC5` = as.numeric(dist_m[,6]))
         
# Replace 0 with NA
df2/1610
```

###Remark:The distance between Dealer 21716 and VDC 3F	4J	7J	7M	BC are 719,683, 688,817,365miles.

##Slide 4:Calculation of The Total costs
###Equition of total cost
###AV: Sum of {[(Distance between Plant-VDC)+(Distance between VDC-Dealer)]*0.55 +40}*Qijk
###Truck: Sum of {[(Distance between Plant-VDC) + (Distance between VDC-Dealer)]*0.1*4 +200*0.1 +50}*Tijk
This part calculated the total cost of shiping all demanded cars from Plant1 and 2 through VDC1-5 to Dealer 1 and 2. The lp file contains the objective function and constraints. The objective function is the total cost equation. Qijk means the quantity of cars shiped from Planti through VDCj to Dealer K by AV (car itself). For example, Q211 means the number of cars shiped from plant1-3A through VDC1-3F to Dealer1-21720. Since given by the problem that the cost of shiping one car from plant to dealer equals to the cost of shiping cost + VDC handling cost per car= 0.55 dollars per miles per car + 40 dollars per car.The total demand of cars from plant1 to dealer1 is 212 cars. Then the total cost of shiping of Plant1-Dearler1 is [(902+739)*0.55+40]*Q111. The Tijk means the number of cars shiped from Plant i through VDCj to Dealer K by truck. Each truch can contain max of 10 per load.The same example as shiping type of AV, the total cost of shiping by truck is (distance*0.1*4 +200*0.1 +50)*T111. The 0.1 means the 10 cars per load, and 4 is the 4 dollars per load per mile. 200 dollar is the 

##Slide 5:LP file
###Objective function:
####min: 942.55 Q111 + 726.4 T111 + 891.95 Q121 + 689.6 T121 + 924.4 Q131 + 713.2 T131 + 974.45 Q141 + 749.6 T141 + 904.6 Q151 + 698.8 T151 + 567.45 Q211 + 453.6 T211 + 434.35 Q221 + 356.8 T221 + 450.3 Q231 + 368.4 T231 + 396.95 Q241 + 329.6 T241 + 940.35 Q251 + 724.8 T251 + 931.55 Q112 + 718.4 T112 + 1157.05 Q122 + 882.4 T122 + 993.15 Q132 + 763.2 T132 + 1099.3 Q142 + 840.4 T142 + 582.3 Q152 + 464.4 T152 + 556.45 Q212 + 445.6 T212 + 699.45 Q222 + 549.6 T222 + 519.05 Q232 + 418.4 T232 + 521.8 Q242 + 420.4 T242 + 618.05 Q252 + 490.4 T252;
###Constraints:
###Demand of Plant-Dealer
Demand of Plant-Dealer
Plant\Dealer	Dealer1	Dealer2
Plant1	212	14
Plant2	90	40

###Explaination of constraints:

Q111 + T111 + Q121 + T121 + Q131 + T131 + Q141 + T141 + Q151 + T151 = 212;
Q211 + T211 + Q221 + T221 + Q231 + T231 + Q241 + T241 + Q251 + T251 = 90;
Q112 + T112 + Q122 + T122 + Q132 + T132 + Q142 + T142 + Q152 + T152 = 14;
Q212 + T212 + Q222 + T222 + Q232 + T232 + Q242 + T242 + Q252 + T252 = 40;


###Integer
TT111 = 0.1 T111;
TT121 = 0.1 T121;
TT131 = 0.1 T131;
TT141 = 0.1 T141;
TT151 = 0.1 T151;
TT211 = 0.1 T211;
TT221 = 0.1 T221;
TT231 = 0.1 T231;
TT241 = 0.1 T241;
TT251 = 0.1 T251;
TT112 = 0.1 T112;
TT122 = 0.1 T122;
TT132 = 0.1 T132;
TT142 = 0.1 T142;
TT152 = 0.1 T152;
TT212 = 0.1 T212;
TT222 = 0.1 T222;
TT232 = 0.1 T232;
TT242 = 0.1 T242;
TT252 = 0.1 T252;
int TT111, TT121, TT131, TT141, TT151, TT211, TT221, TT231, TT241, TT251, TT112, TT122, TT132, TT142, TT152, TT212, TT222, TT232, TT242, TT252;

```{r}
library(lpSolveAPI)
gp1 <- read.lp("Group4projectfinal.lp")
gp1
```

##Slide 6: Shipping Cost, number and path

```{r}
solve(gp1)
get.objective(gp1)
```
### Total cost: 
###$199973.1
This results shows the total cost of shiping all cars reguqired from Plant1-2 to Dearler1-2.
Based on the given data, the requirment of Plant1-3A to Dealer1-21720 is 212, the requirment of Plant2-FF to Dealer1-21720 is 90, the requirment of Plant1-3A to Dealer2-21716 is 14, the requirment of Plant2-FF to Dealer2-21716 is 40.The smallest total cost is 182473.1 dollars.

### Number and path:

###Q121=2, T121=210, T241=90, Q152=4, T152=10, and T232=40.
 
```{r}
get.variables(gp1)
```

The results shows the best shiping patch of this combination of plants and dealers. Follow the order of variables we can get that: Q121=2, T121=210, T241=90, Q152=4, T152=10, and T232=40. The result shows that the VDC2-4J is the best VDC for shipping between Plant1-3A and Dealer1-21720 (2 by AV, 210 by truck), the VDC4-7M is the best VDC for shipping between Plant2-FF to Dealer1-21720 (90 by truck), the VDC5-BC is the best VDC for shipping between Plant1-3A to Dealer2-21716 (4 by AV, 10 by truck), and the VDC3-7J is the best VDC for shipping between Plant2-FF to Dealer2-21716 (40 by truck).

##Slide 7: The Third Method: Rail

###Rail cost Equation
###Sum of {[(Distance between Plant-VDC) + (Distance between VDC-Dealer)]*0.05*3 +2000*0.05 +50}*Rijk

##Slide 8: The Limitation of Time
###The limitation of time:
###Will affect the number of demand and change the number of constraints.
####Q111 + T111 + Q121 + T121 + Q131 + T131 + Q141 + T141 + Q151 + T151 = DP1D1; 
####Q211 + T211 + Q221 + T221 + Q231 + T231 + Q241 + T241 + Q251 + T251 = DP2D1; 
####Q112 + T112 + Q122 + T122 + Q132 + T132 + Q142 + T142 + Q152 + T152 = DP1D2;
####Q212 + T212 + Q222 + T222 + Q232 + T232 + Q242 + T242 + Q252 + T252 = DP2D2;
###Will affect the shipping method since the shipping with rail is slower than other two methods.
####Shipping time equation: 
####AV&T:[(Distance between Plant-VDC) + (Distance between VDC-Dealer)]/30
####Rail:[(Distance between Plant-VDC) + (Distance between VDC-Dealer)]/10


##Slide 9:The Capacity of VDC
###The capacity of VDC
###Will affect the number of cars transported through each VDC and change the number of constraints.
###Add the penalty and time limited.
####Q111 + T111 + R111 + Q121 + T121 + R121 + Q131 + T131 + R131 + Q141 + T141 + R141 + Q151 + T151 + R151 = DP1D1; Q111 + T111 + R111 <= C1;